Station summary

### 2023-02-09 reports/02_stations.qmd
Start looking at zooplankton

---
title: "Predator summary"
format:
  html:
    code-fold: true
editor: visual
output-dir: "docs"
---

@@

tar_load(c("predators_agg", "sg_sf"), store = here::here("_targets"))
source(here::here("R", "sp.R"))
```

## South Georgia winter predators

### Counts

The six most abundant species.

>>>>

---
title: "Station summary"
format:
  html:
    code-fold: true
editor: visual
output-dir: "docs"
---

@@

tar_load(c("zoop"), store = here::here("_targets"))
# source(here::here("R", "sp.R"))
```

## Station maps

By year.
